\TheTitle

### 2017-06-19 paper/abstract.tex
Minor rewording in abstract
Natively -> Internally; There are no other options

Fixes spelling of alleviate

Places TODO in a notice command.

Natively, git uses a directed acyclic graph model (DAG) with references
pointing from the most recent commit (TODO: most recent commit?, it's
not the \emph{HEAD} because that moves around) toward the initial commit
in the repository. This model is useful and necessary to the internal
functionality of the version control system, but does not provide users
with a clear nderstand of the events occuring in the repository. Due to
the direction of the link in the DAG, visualziation tools, like gitk,
are unable to provide summarized aggregation of the commits at a given
merge.  Furthermore, the visual DAG does not provide a clear explanation
of the events taking place in the repository.

Merge-Trees are a data structure derived from the DAG, that could
potentially alleiveate the issues with visualization built directly from
the DAG. The trees are defined such that the root is the merge into the
master branch, and the leaves are the individual commits. The references
point in both directed, from each node to the parent, and from the
parent to the children. Depending on the complexity of the merge, the
path from leaf to root may pass through multiple internal nodes.

>>>>

Internally, git uses a directed acyclic graph model (DAG) with references
pointing from the most recent commit \notice{(TODO: most
    recent commit?, it's not the \emph{HEAD} because that moves
    around)} toward the initial commit in the repository. This model is
useful and necessary to the internal functionality of the version
control system, but does not provide users with a clear nderstand of the
events occuring in the repository. Due to the direction of the link in
the DAG, visualziation tools, like gitk, are unable to provide
summarized aggregation of the commits at a given merge.  Furthermore,
the visual DAG does not provide a clear explanation of the events taking
place in the repository.

Merge-Trees are a data structure derived from the DAG, that could
potentially alleviate the issues with visualization built directly from
the DAG. The trees are defined such that the root is the merge into the
master branch, and the leaves are the individual commits. The references
point in both directed, from each node to the parent, and from the
parent to the children. Depending on the complexity of the merge, the
path from leaf to root may pass through multiple internal nodes.
